% hello.tex - Our first LaTeX example!

\documentclass{article}

\begin{document}
\begin{abstract}
The goal of this exercise is to show that you know how to use LaTeX, not that you are a prolific writer.
\end{abstract}

\section{Personal History}

My name is Adil Khan. I am currently pursuing my Masters in Computer Science from SJSU. Previously, I have done my Bachelors in Computer Engineering from Pune University. Through my academic coursework and professional career, I have gained expertise in diverse fields of Computer Science such as DevOps, Android Development, Machine learning and Big Data. So I’m very flexible with learning new technologies and implementing solutions.
I'd really describe myself as a person with a versatile skill-set, a lot of integrity and a willingness to go the extra mile to get the desired solution.

\section{Academic/Career Goals}
\label{sec:one}

\begin{enumerate}
\item To move into a position of responsibility and build a cloud deployment pipeline for a company.
\item To secure good grades in this course.
\item To work on an interesting project to show on my Resume.
\end{enumerate}

\section{Research Topics of Interest}
As mentioned in Section ~\ref{sec:one},I have strong interests in the field of cloud deployment, DevOps and machine learning. 
As a research topic, I would love to explore about possibilities of using Machine learning to improve Cloud infrastructure.
I have found this paper ~\cite{DBLP:conf/ccs/GulmezogluES17} and this paper ~\cite{DBLP:conf/cscloud/SalmanBEJS17} for the same.

\bibliography{hello}{}
\bibliographystyle{plain}

\end{document}